Temporal Development of Overlapping Communities in Co-Authorship Networks

### 2016-01-02 paper/paper.tex
last img

\subsubsection{(4) Each connected component in the clique graph form a $k$-clique-community.}
In the resulting graph we need to look for connected components, those represent the $k$-clique-communities, see figure~\ref{fig:result}.

@@

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\textwidth]{result}
		\caption{Here the two resulting $k$-clique-communities are shown.}
		\label{fig:result}
\end{center}
\end{figure}

>>>>

\subsubsection{(4) Each connected component in the clique graph form a $k$-clique-community.}
In the resulting graph we need to look for connected components, those represent the $k$-clique-communities, see figure~\ref{fig:final}.

@@

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\textwidth]{img/final}
		\caption{Here the two resulting $k$-clique-communities are shown.}
		\label{fig:final}
\end{center}
\end{figure}
